Behavior Driven Development in Haskell

### 2012-06-02 paper.tex
Specs -> Spec

\begin{quote}
\small
\begin{verbatim}
shouldSatisfyMonoidLaws ::
  (Eq a, Show a, Monoid a, Arbitrary a) => a -> Specs
shouldSatisfyMonoidLaws t = do
  describe "mempty" $ do
    it "is a left identity" $ property $ \x ->
      mempty <> x == x `asTypeOf` t

>>>>

\begin{quote}
\small
\begin{verbatim}
shouldSatisfyMonoidLaws ::
  (Eq a, Show a, Monoid a, Arbitrary a) => a -> Spec
shouldSatisfyMonoidLaws t = do
  describe "mempty" $ do
    it "is a left identity" $ property $ \x ->
      mempty <> x == x `asTypeOf` t
